\pkg{webchem}: An \proglang{R} Package to Retrieve Chemical Information from the Web

### 2020-04-03 revision3_2581/paper.tex
Updated Fig.3 description

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.7\textwidth]{plot_qsar-1} 
  \caption{Simple QSAR for predicting log LC\textsubscript{50} of
    pesticides by the ocatanol-water partitioning coefficient $\mathrm{log}~\mathit{P_{oct/wat}}$.
    $\mathrm{log}~\mathit{P_{oct/wat}}$ values have been retrieved from the Pubchem
    database (118 estimated data and 6 substances without data).  Blue line
    indicates the regression model
    ($\mathrm{log~LC}_{50} = 2.86\ensuremath{-0.36}~\mathrm{log}~P$,
    RMSE = 1.47). The x-axis is shown not logarithmized.}
\label{fig:fig3}
\end{figure}

>>>>

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.7\textwidth]{plot_qsar-1} 
  \caption{Simple QSAR for predicting log LC\textsubscript{50} of
    pesticides by the ocatanol-water partitioning coefficient $\mathit{P_{oct/wat}}$.
    $\mathrm{log}~\mathit{P_{oct/wat}}$ values have been retrieved from the Pubchem
    database (118 estimated data and 6 substances without data).  Blue line
    indicates the regression model
    ($\mathrm{log~LC}_{50} = 2.86\ensuremath{-0.36}~\mathrm{log}~P$,
    RMSE = 1.47).}
\label{fig:fig3}
\end{figure}
